---
title: "Data Analyzing"
author: "Akarin Luckanasub"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### **Data Overview**
##### First, let's take a look at the flights dataset:

```{r}
library(tidyverse)
library(nycflights13)
view(flights)
data("flights")
data("airlines")

```

### **Q1: Most Flight Carrier in September 2013**
##### The following code finds the top 5 flight carriers in September 2013:

```{r}
flights %>%
  filter(month == 9, year == 2013) %>%
  count(carrier) %>%
  arrange(desc(n)) %>%
  head(5) %>%
  left_join(airlines, by = "carrier")

```

### **Q2: Top 10 Airlines with the Most Flight Distance**
##### This code identifies the top 10 airlines that have the most flight distance:

```{r}
flights %>%
  left_join(airlines, by = "carrier") %>%
  select(name, carrier, distance) %>%
  group_by(name) %>%
  summarise(total_distance = sum(distance, na.rm = TRUE)) %>%
  arrange(desc(total_distance)) %>%
  head(10)

```

### **Q3: Top 10 Airlines with the Longest Flight Time**
##### The following code lists the top 10 airlines with the longest flight time:

```{r}
flights %>%
  left_join(airlines, by = "carrier") %>%
  select(name, carrier, hour) %>%
  group_by(name) %>%
  summarise(total_time = sum(hour, na.rm = TRUE)) %>%
  arrange(desc(total_time)) %>%
  head(10)

```

### **Q4: Top 10 Airlines with the Most Air Time**
##### This code finds the top 10 airlines with the most air time:

```{r}
flights %>%
  left_join(airlines, by = "carrier") %>%
  select(name, carrier, air_time) %>%
  group_by(name) %>%
  summarise(total_air_time = sum(air_time, na.rm = TRUE)) %>%
  arrange(desc(total_air_time)) %>%
  head(10)

```

### **Q5: Top 10 Airlines with the Most Arrival Delays**
##### The code below identifies the top 10 airlines with the most arrival delays:

```{r}
flights %>%
  left_join(airlines, by = "carrier") %>%
  select(name, carrier, arr_delay) %>%
  group_by(name) %>%
  summarise(total_arr_delay = sum(arr_delay, na.rm = TRUE)) %>%
  arrange(desc(total_arr_delay)) %>%
  head(10)

```









